Performance of two different ontological and data access methods

### 2014-07-02 cold2014/magnus.tex
challenges to validity
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@712 43ef1190-90fd-4dd7-a769-d0121f02b80e

\section{Pros and cons}
There are several ways of making an application handle PDPs. As
mentioned there can be differences in collecting data, presenting data
and using data. This means that a recommended ontology and data
representation needs to be robust. This means that it has to be able
to perform well under different scenarios.  The ideal semantic
situation would not rely on string comparison, but with both
ontologies one have to deal with string literals eventually. A string
literal is still the value a user is presented with.  It depends on
how much of the data one wants machine accessible and how much is for
internal human reading.

@@

>>>>

\subsection{Pros and cons}
There are several ways of making an application handle PDPs. As
mentioned there can be differences in collecting data, presenting data
and using data. This means that a recommended ontology and data
representation needs to be robust. This means that it has to be able
to perform well under different scenarios.  The ideal semantic
situation would not rely on string comparison, but with both
ontologies one have to deal with string literals eventually. A string
literal is still the value a user is presented with.  It depends on
how much of the data one wants machine accessible and how much is for
internal human reading.

@@

\subsection{Challenges to validity of methodology}

There are several challenges to the validity of present
study. Following the discussion of \cite{publication-9417}, we
think that the most important problem to the internal validity is
related to the ordering of which the specifications are queried. We
have argued that the order is important, but we have not investigated
whether a change of the order will affect the overall performance.

The main challenge to construct validity is the choice of factors in
the large scale experiments: Even though a 10 factor experiment is a
large full factorial experiment, and although the most significant
factors are the same in all experiments, we have not investigated
whether other factors could influence the result as much.

Since the present study represents a common use case for Semantic Web
application, we are of the opinion that there is a strong case for its
external validity, but it does obviously rely on that the study itself
is valid.
